\subsubsection{Terminology}

%%% Background knowledge
% What is GUI test case
% What is current state
% What is GUI model

A Graphical User Interface is a  forest hierarchical windows that only one of them at a time is active to be used.  
Windows includes atomic element named widget that are characterize by attribute, such as text or locations.
At any time the active window has a sate that encompasses attribute values of all visible widgets.
Type of widget depends on their functionality and some of them expose user-actionable events for users to interact with the application.

A GUI event is an atomic humane-computer interaction, such as click on a widget with the type button or fill an editable widget.
An oracle event check the state of a widget. 
For example, if a widget displays a specific text. 
A GUI test is a sequence of events $\langle e_1,..., e_n\rangle$ on widgets of active windows.
A test execution results transitioning the state of the active windows $S_{0} \xrightarrow{e_1} S_1 \xrightarrow{e_2} S_2 \ldots \xrightarrow{e_n} S_{n}$ 
%\), 
where $S_{i-1}$ and $S_i$ denote the states of the active window before and after the execution of $e_i$, respectively. 
A GUI model (\tam) is a directed graph where node correspond to GUI states  and edges correspond to events that transition the the source node (state before event) to the target node (state after the event).
% Test Reuse
% Semantic matching is one-to-one and using GUI model alleviate this issue.
% What is stepping events

\testreuse is the process of migrating test cases across apps with similar functionalities. 
\testreuse relies on semantic matching to find a corresponding event from the source test case in the target applications (one-to-one matching). 
Semantic matching uses textual attributes of widgets to score similarity of events.
The target test case may include stepping events, that are event not corresponding to any event in source test case.
The stepping event are required to reach relevant states.
The source test case may include  unmatchable events, that are event not corresponding to any event in target test case.
\testreuse handles stepping and unmatchable by relying on \tam.


