\subsection{Schedule and milestones}
% 1000 words

\input{tables/schedule-table.tex}

Table~\ref{tab:research-plan} summarizes the schedule and milestones of the \project project.
We will achieve a milestone corresponding to an objective by completing three steps: Study, Experiment, and Report. 
 In the study phase, we will review the related works.
In the experiment phase, we will gather: a complete data set for training models, build a new \testreuse approach, and empirically evaluate the approach. 
In the report phase, we will submit the results of experimenting with our approaches in  the top research venues in Software Engineering.
%We explain the details of milestones below.

\smallskip
\noindent
\textbf{O1: Incorporating Internal Resources:}  

\noindent
In the study phase, we will review vision-based GUI testing~\cite{Hu:appflow:FSE:2018,zhao:Avgust:FSE:2022,YazdaniBanafsheDaragh:DEEPGUI:ASE:2021}  and widget recognition approaches~\cite{white:WidgetDetection:ISSTA:2019,zhu2021widgetrecog}. 
We will examine the replication package and data sets of these studies, and in case of compatibility with our context, we will reuse them. 
Otherwise, we will study image captioning and classification approaches to build our model for the \imagelabeler component.
%\bigskip
%There is a risk that existing approaches for recognition of widgets will not be replicable. 
%In that case we need to take an alternative route which is classifier type, building training set, and training a classifier.  
%Therefore, we study computer vision approaches to identify most suitable classifier. 
%The most common approach for image classification is Convolutional Neural Networks (CNN)~\cite{lecun1995convolutional}. 
%Using CNN requires careful choice of its architecture depending on the down stream tasks. 
%We will investigate the most popular choices that includes: ResNet~\cite{he:ResNet:CVPR:2016}, Inception~\cite{szegedy:inception:CVPR:2015}, MobileNet~\cite{howard:mobilenets:arxiv:2017}.
%
%\bigskip

\smallskip
We will transition from the study to the experiment phase by conducting a feasibility study. 
%We will investigate from suitable approaches that we identified which one is more promising in our context.
We will select the most promising technique for labeling  widgets that is suitable in our context.  
To do so, we will experiment with different prototypes of \imagelabeler for semantic matching in isolation from the \testreuse,  similar to our previous study~\cite{mariani:SemFinder:ISSTA:2021}. 
Then, we will integrate \imagelabeler in our \tme framework to create a new \testreuse approach named \visiontool\footnote{Horus is a god in ancient Egyptian mythology that symbolizes heightened vision.}.
Additionally, we will use our~\tme framework to evaluate \visiontool and compare with the state-of-the-art \testreuse approaches.

\smallskip
Finally, we will submit the results of our  feasibility study to a workshop conference and the result of the \testreuse experiments to a top software engineering conference. 

%%% O2


\smallskip
\noindent
\textbf{O2: Incorporating External Resources:}  

\noindent
In the study phase, we will review LLM-based GUI testing approaches~\cite{Zimmermann:GPT3GUITest:2023:ICSTW, liu:GUIInputLLM:ICSE:2023} and prompt engineering, as a recent study shows tuning prompts improve specialised tasks such as code summarization  by 26\% on average~\cite{wang:prompt:FSE:2023}.
%\bigskip

\smallskip
We will transition from the study phase to the experiment phase by conducting a feasibility study that examines different LLM models and prompt patterns.
%We will investigate the applicability of existing LLM models in our context and if they require fine-tuning.
We will examine different combinations of LLM models and prompt patterns to translate a limited number of test cases.
We will manually inspect their quality and choose the most promising combination.
After the feasibility study, we will integrate the \llmtranslator into our framework to create a new \testreuse approach named \llmtool\footnote{Hermes is a god in ancient Greek mythology that symbolizes linguistic prowess.}.
Additionally, we will use our \tme framework to evaluate \llmtool and compare with the state-of-the-art \testreuse approaches.

\smallskip
Finally, we will submit the results of our  feasibility study to a workshop conference and the result of the \testreuse experiments to a top software engineering conference. 


%%% O3


\smallskip
\noindent
\textbf{O3: Improving Robustness:}  

\noindent
%study
In the study phase, we will review Reinforcement Learning based  GUI testing approaches~\cite{Pan:QTesting:ISSTA:2020,Romdhana:ARES:TOSEM:2022}. 
We will identify suitable options for the RL techniques, state presentation, and reward function.
%Experiment

\smallskip
We will transition from the study to the experiment phase by  conducting a feasibility study, in which we evaluate the candidate \rlaganets performance based on the number of distinctive windows  explored in a given amount of time. 
After the feasibility study, we will  integrate the best \rlaganet in our framework to create a new \testreuse approach named \rltool\footnote{Athena is a goddess in ancient Greek mythology that symbolizes strategic intellect.
}.
\rltool subsumes \visiontool and \llmtool by  encompassing \imagelabeler and \llmtranslator components.
Additionally, we will use our \tme framework to evaluate \rltool and compare with the state-of-the-art \testreuse approaches.
%We will evaluate the effectiveness of \rlaganet in three setups:
%\begin{inparaenum}[a)]
%	\item The agent only executes before \testreuse to make GUI model more complete
%	\item The agent only executes when semantic matching is uncertain
%	\item The agent executes both in the beginning and uncertain conditions.
%\end{inparaenum}

\smallskip
Finally, we will submit the \rltool in a tool track of a conference and the result of the \testreuse experiments in a top software  engineering journal to conclude the project. 
















