\subsection{Current state of research in the field }
%1000 words

\input{sections/background.tex}

% Non semantic appraoches 

% Patter-based
% Test Reuse
% leveraging vision for test generation in random, pattern , ..
% Leveraging LLM for test generatoin,input, but no GUI


% What is LLM?

% All approaches
\subsubsection{State of the art}
GUI testing has been a popular field in software engineering for more than two decades. Researchers proposed many approaches that we classify into four categories:
 random-based, model-based, coverage-based, and  similarity-based.
Random-based approaches take random actions to interact with  the GUI~\cite{machiry:dynodroid:FSE:2013,vos:testar:ijismd:2015,ermuth:monkey:ISSTA:2016}.
Model-based approaches build a GUI model and generate test cases that cover the mode based on a coverage criteria~\cite{Nguyen:GUITAR:ASEJ:2014,Li:DroidiBot:ICSE-C:2017,Gu:PractivalTest:ICSE:2019,Choi:swift:OOPSLA:2013}. 
Coverage-based approaches employ search based algorithm~\cite{Gross:exist:ISSTA:2012,mahmood:evodroid:FSE:2014,dong:TimaMachine:ICSE:2020} or symbolic execution  to generate test cases that maximizes code coverage~\cite{Ganov:GUIsymbolic:FMSE:2009,cheng:guicat:ASE:2016,Anand:conc:FSE:2012}.
Similarity-based approaches use existing knowledge of testing a functionality of applications to generate test cases for applications with similar functionalities.
All of the categories except for similarity-based are agnostic to semantics of the application under the test. 
Non-semantic approaches generate many test cases quickly with high coverage, but they only reveal crashing faults and cannot expose functional faults.

% Pattern-
\smallskip 
Millions of applications share similar functionalities that create an opportunity of testing them in similar way.
For example, online booking of flights can be tested similarly across different applications. 
Similarity-based approaches leverage this opportunity and generate test cases relevant to functionality of the applications.
We classify similarity-based approaches into pattern-based and \testreuse.
Pattern-based approaches consider patterns comprising abstract recurrent events and match  elements of the pattern to actual events in the target application~\cite{Moreira:pattern:ISSRE:2013,Morgado:Impact:HCI:2019}.
They either consider a predefined set of patterns~\cite{Mariani:Augusto:ICSE:2018,Hu:appflow:FSE:2018}, or automatically extract patterns from traces of user interactions~\cite{linares:mining:MSR:2015,mao:crowd:ASE:2017,Mao:UserPattern:JSS:2021}.
Crafting pattern manually requires substantial human effort, and extracting patterns automatically requires huge data.


\smallskip 
\testreuse approaches leverages semantic similarity of textual information available in the GUI to migrate test cases of an application (source) to another (target).
Researchers proposed approaches to migrate test cases of the same  application across different platforms and different applications in the same platform. 
TestMig migrates test cases from IOS version of an app to its Android version~\cite{Qin:testmig:ISSTA:2019}.
MAPIT migrates test cases bidirectionally between IOS and Android versions of the same app~\cite{talebipour:MAPIT:ASE:2021}.
TransDroid migrates test cases of web apps to their Android version~\cite{lin:TransDroid:ICST:2022}.
 Rau et al. proposed migrating test cases in web applications by using semantic matching of GUI elements~\cite{rau:efficent:icse:2018}.
 \craftdroid migrates test cases across Android apps~\cite{lin:craftdroid:ASE:2019}.
GUITestMigrator migrates test cases between prototype apps that share the same specifications.
\atm is an extension of GUITestMigrator that mitigate test cases of real apps~\cite{Behrang:migration:ICSE:2018}.
 \adaptdroid formulates \testreuse as a search problem and uses an evolutionary algorithm to explore the space of possible GUI test cases~\cite{Mariani:Adaptdroid:AST:2021}.
 
 
\smallskip 
Researchers exploited Machine Learning techniques to propose enhanced approaches in different categories of GUI test generation.
%Vision
APPFLOW uses computer vision to match elements of predefined patterns to elements of the GUI in the target application~\cite{Hu:appflow:FSE:2018}.
AVGUST leverages computer vision to extract patterns from screen recording of users interacting with apps~\cite{zhao:Avgust:FSE:2022}.
White et al. proposed a random approach that detects type of widgets from their visual appearance~\cite{white:WidgetDetection:ISSTA:2019}.
%%%%Their approach determines the widget type, such as the menu or text box. However, it does not provide information about the semantics of widgets.
Zhu et al proposed an approach for identifying the intent of widgets~\cite{zhu2021widgetrecog}.
%%%%However, their approach is not examined in the GUI testing context. 
% RL
DeepGUI uses deep reinforcement learning (RL) and computer vision to identify actionable events and select them~\cite{YazdaniBanafsheDaragh:DEEPGUI:ASE:2021}.
Some approaches used reinforcement learning  to model behavior of the GUI and select events. 
AutoBlackTests~\cite{Mariani:ABT:STVR:2014} and A-test~\cite{Vuong:RLTest:A-Test:2018} use Q-Learning to generates test cases  for desktop and Andoroid apps, respectively.
ARES uses deep learning to infer states similarities while previous approaches used tabular reinforcement learning~\cite{Romdhana:ARES:TOSEM:2022}.
Recently Large Language Models (LLM) have been used to generate inputs for editable widget in random GUI testing~\cite{liu:GUIInputLLM:ICSE:2023}, and to transform natural language commands into GUI test cases~\cite{Zimmermann:GPT3GUITest:2023:ICSTW}. 

% limitations of current test reuse approaches

\smallskip 
%\testreuse approaches are the most recent category of GUI test generation approaches.
%They provide a great opportunity to create realistic test cases that can expose functional faults. 
\testreuse approaches are the most recent category of GUI test generations, which they can expose functional faults by exercising realistic scenarios.
%However, current approaches have limitations that hinders their potential. 
Our review of state of the art and our empirical studies of \testreuse~\cite{mariani:SemFinder:ISSTA:2021,khalili:DomainEmbedding:ICPC:2022} suggest  we can address limitations of current approaches by using advanced machine learning techniques.
%First limitation is that they only rely on textual information in the GUI to semantically matches events of two applications. 
First limitation is that the current \testreuse approaches ignore visual information and thye only rely on text, which may not be sufficient. 
%In this project we plan to leverage computer vision to address this limitation by combining visual and textual information.
In this project we will leverage computer vision to address this limitation by combining visual and textual information.
%Additionally, we will use LLM models to incorporate external information into \testreuse. 
Additionally, we will use LLM models to incorporate web information that is integrated in them to improve \testreuse. 
%Second limitation is current approaches navigate in the target application by relying \tam that often is incomplete. 
Second limitation is that current approaches explore the target application by relying on \tam that is often incomplete.
%In this project we plan to use Reinforcement Learning to create a more comprehensive \tam.
In contrast to model-based approaches that replaced the \tam with an RL agent, in this project we will use RL to create a more comprehensive model.


\subsubsection{Current Research Projects}
Software testing is an important topic that is subject of many research projects.
The most relevant research projects that applicant is aware of includes:
\textit{Testing the Untestable} (P.I. Lionel Briand), and
\textit{Self-assessment Oracles for Anticipatory Testing} (P.I. Paolo Tonella) are focus on problem of testing machine learning, while this project use machine learning to to test GUI applications.
\textit{A-Test Autonomic Testing} (P.I. Mauro Pezze) focuses on testing distributed systems in the production environment, which also uses machine learning but for different type of application in different environment. 
The first two project are funded by are ERC and last one by SNF.



% Sam approache propose a general faremwork targets transfering test cases and complement current test reuse approaches by intergrating other category of test case generation such as model-based testing. While this project aims to address limitation of current test reuse approaches by leveraging artificial intelligence.