	\section{Summary of the research plan}
	%1000 words
	% What should be included in here? summary of all below sections?


% What problem project aims to solve?
In this project, we define a set of approaches to automatically test applications through their Graphical User Interface (GUI). 
Our approaches generate test cases that exercise the application under the test with realistic scenarios and reveal functional faults. 


% What is the gap in the research?
Testing applications is a crucial step in the development process that increases the quality of the application.
GUI testing tests applications at the integration level to ensure their compliance with the functional requirements. 
Generating test cases manually (the common industry practice) is a tedious task that bears a substantial cost to organizations. Most automated approaches only maximize code coverage and reveal faults that lead to system crashes.
However, they ignore the functionality of applications and miss the functionality related faults. 
Recently, researchers proposed approaches, such as \testreuse, that are aware of the semantics of applications, and they generate test cases that exercise the functionalities similarly to users. 


\testreuse is a promising category of automated GUI testing approaches that migrate test cases of an application to another with similar functionalities. These approaches are recent, and they have limitations. 
Thus, they require improvement to be fully applicable in industrial environments. The current \testreuse approaches are inaccurate in migrating test cases due to merely relying on textual information in the GUI for inferring semantics and poor decision-making strategies for dealing with the lack of information. 


% What are the objectives? We do X to Y
In this project, we will address the current limitations of \testreuse approaches by
\begin{inparaenum}[(i)]
\item using visual information of GUI to enrich internal information used in the test migration,
\item using patterns of GUI interactions and web information to incorporate external information,
\item defining strategies to build comprehensive models of GUI that facilitate navigation and decision making of \testreuse approaches.
\end{inparaenum}

% How we do that? We use technique W to do X

We will leverage Artificial Intelligence to define and integrate a set of \testreuse approaches to create a  \textbf{H}ighly \textbf{In}telligent \textbf{Te}st \textbf{R}euse (\project) approach.
We will use 
\begin{inparaenum}[(i)]
\item Computer Vision to extract visual information in the GUI,
\item  Large Language Models to integrate their vast knowledge and pattern recognition capabilities,
\item Reinforcement Learning to efficiently build models for  GUI of applications.
\end{inparaenum}
% How we validate the approach?
We will validate our approaches on the most popular applications from different domains to demonstrate their general applicability and effectiveness in the industrial environment.


% What is the impact of the project?

This project will impact both research and industry. 
It will impact research in software engineering by introducing approaches that generate test cases at the integration level and methods that benefit other testing areas, such as test repair. 
It will impact the development of software applications by increasing their quality and reducing production costs.




























